Experiences designing and building a PRAGMA Cloud Scheduler

### 2015-08-14 paper.tex
Merged copy

\maketitle
\begin{abstract}
The Pacific Rim Application and Grid Middleware Assembly (PRAGMA) is a community of research scientists and institutions from around the Pacific Rim that work together to enable scientific expeditions in areas of biodiversity distribution and lake ecology.  Over the past four years, the technology focus for PRAGMA partners has shifted to cloud and software defined networking as enabling technologies.  During PRAGMA 27 meeting, the Resources Working Group discussed rebooting the persistent PRAGMA Testbed as a way for sites to contribute and use shared resources, leveraging technologies such as PRAGMA Boot, Personal Cloud Controller (PCC), and virtual network overlays (i.e. IPOP and ViNe).  To make PRAGMA resource sharing easier, a lightweight scheduler was proposed and discussed as a way to enable access to the resources and to manage resources reservations.  This short paper discusses the design process and initial prototype of a simple cloud scheduler for PRAGMA.

@@

PRAGMA researches actively collaborate to enable scientific expeditions in areas of computational chemistry, telescience, biodiversity, and lake ecology~\cite{pragmaWeb}.  Founded in 2002, PRAGMA originally sought to advance the use of grid technologies in applications among a community of investigators working with leading institution sites around the Pacific Rim~\cite{pragmaReport2004}.  This included the deployment of a shared PRAGMA Grid testbed where participating sites could contribute and use resources as needed to develop and test new middleware and to conduct scientific experiments.  Testbed sites needed to install at a minimum Globus~\cite{globus} and a local HPC job scheduler as well as other optional software such as MPICH-G2~\cite{mpichg2} and Ninf-G~\cite{ninfg}.  In November 2006, nineteen sites in thirteen countries were part of the testbed.  By 2009, the testbed had grown to twenty-seven sites in fifteen countries with a total of 1008 CPUs, more than 1.3 terabytes of memory, and over 24.7 terabytes of online storage.  However, as of 2011, the number of sites started to decline and maintaining the numerous and complex middleware and scientific applications at each local site required significant people effort and expertise.  Since PRAGMA participants often have varying levels of of funding, staff, and expertise, PRAGMA started to shift away from grid towards cloud technologies to simplify the infrastructure and to lower the amount of effort any site would need to participate in the testbed.

@@

One category of tools we looked at were plugins to existing frameworks like Drupal~\cite{drupal} and Wordpress\~cite{wordpress}.  We looked at Booking_calendar for Wordpress as well as Merci and Reservations for Drupal   
One category of tools that we looked at were developed in PHP and had a relational backend database such as Postgres an MySQL.  We looked at Meeting Room Booking System on SourceForge~\cite{mrbs}, Booked from Twinkle Toes Software, and Classroombookings on Github,

@@

 tried a few tools  here is the summary:
1. OTA hotel management   http://rocks-86.sdsc.edu/hotelmis/setup/initialsetup.php
    appears to be just for the hotel, no easy login, no easy change. Not useful
2. Mybooking - in Malay and after changing the language and trying enenglishigsh i did not get far. -- hotel
3. Booking_calendar - strictly room booking, very small in features, too much to rewrite. -- wordpress plugin
4 Optaplanner appears to be a java app that runs outside of web. I tried examples and i am
   not sure of its usability. The examples are running producing sometimes some output sometimes noe
   and they are just java apps on some data. The examples  are not impressive even in terms of giving
   an idea how things are run.

>>>>

\maketitle
\begin{abstract}
PRAGMA is a community of research scientists and institutions from around the Pacific Rim that work together to enable scientific expeditions in areas of biodiversity distribution and lake ecology.  Over the past four years, the technology focus for PRAGMA partners has shifted to cloud and software defined networking as enabling technologies.  During PRAGMA 27 meeting, the Resources Working Group discussed rebooting the persistent PRAGMA Testbed as a way for sites to contribute and use shared resources, leveraging technologies such as PRAGMA Boot, Personal Cloud Controller (PCC), and virtual network overlays (i.e. IPOP and ViNe).  To make PRAGMA resource sharing easier, a lightweight scheduler was proposed and discussed as a way to enable access to the resources and to manage resources reservations.  This short paper discusses the design process and initial prototype of a simple cloud scheduler for PRAGMA.

@@

The Pacific Rim Application and Grid Middleware Assembly (PRAGMA) researches actively collaborate to enable scientific expeditions in areas of computational chemistry, telescience, biodiversity, and lake ecology~\cite{pragmaWeb}.  Founded in 2002, PRAGMA originally sought to advance the use of grid technologies in applications among a community of investigators working with leading institution sites around the Pacific Rim~\cite{pragmaReport2004}.  This included the deployment of a shared PRAGMA Grid testbed where participating sites could contribute and use resources as needed to develop and test new middleware and to conduct scientific experiments.  Testbed sites needed to install at a minimum Globus~\cite{globus} and a local HPC job scheduler as well as other optional software such as MPICH-G2~\cite{mpichg2} and Ninf-G~\cite{ninfg}.  In November 2006, nineteen sites in thirteen countries were part of the testbed.  By 2009, the testbed had grown to twenty-seven sites in fifteen countries with a total of 1008 CPUs, more than 1.3 terabytes of memory, and over 24.7 terabytes of online storage.  However, as of 2011, the number of sites started to decline and maintaining the numerous and complex middleware and scientific applications at each local site required significant people effort and expertise.  Since PRAGMA participants often have varying levels of of funding, staff, and expertise, PRAGMA started to shift away from grid towards cloud technologies to simplify the infrastructure and to lower the amount of effort any site would need to participate in the testbed.

@@

One category of tools we looked at were plugins to existing frameworks like Drupal~\cite{drupal} and Wordpress\~cite{wordpress}.  We looked at Booking\_calendar for Wordpress as well as Merci and Reservations for Drupal   
One category of tools that we looked at were developed in PHP and had a relational backend database such as Postgres an MySQL.  We looked at Meeting Room Booking System on SourceForge~\cite{mrbs}, Booked from Twinkle Toes Software, and Classroombookings on Github,

@@

 tried a few tools  here is the summary:
1. OTA hotel management   http://rocks-86.sdsc.edu/hotelmis/setup/initialsetup.php
    appears to be just for the hotel, no easy login, no easy change. Not useful
2. Mybooking - in Malay and after changing the language and trying enenglishigsh i did not get far. -- hotel
3. Booking\_calendar - strictly room booking, very small in features, too much to rewrite. -- wordpress plugin
4 Optaplanner appears to be a java app that runs outside of web. I tried examples and i am
   not sure of its usability. The examples are running producing sometimes some output sometimes noe
   and they are just java apps on some data. The examples  are not impressive even in terms of giving
   an idea how things are run.
